A user-extensible and adaptable parser architecture

### 2008-08-11 doc/logparser-background.tex
Dealt with an XXX item - including a sample SQL query instead of duplicating it.

If the database supports sub-selects percentages can be obtained for the
top ten restrictions (sample output shown in \tableref{Truncated sample
output from SQL query showing percentages}):

XXX GENERATE THE FOLLOWING FROM THE SQL FILE FED TO SQLITE\@.

\begin{verbatim}
SELECT restriction_name, hits_total,
        (hits_total * 100.0 /
            (SELECT SUM(hits_total)
                FROM rules
                WHERE postfix_action = 'REJECTED'
            )
        ) || '%' AS percentage
    FROM rules
    WHERE postfix_action = 'REJECTED'
    ORDER BY hits_total DESC
    LIMIT 10;
\end{verbatim}

\begin{table}[ht]
    \caption{Truncated sample output from SQL query showing percentages}
    \empty{}\label{Truncated sample output from SQL query showing
    percentages}
    \begin{tabular}[]{lrr}
        \tableline{}
        Restriction & Number of hits & Percentage of hits \\
        \tableline{}%
        \input{build/include-sample-sql-output}
        \tableline{}
    \end{tabular}
\end{table}

>>>>

If the database supports sub-selects percentages can be obtained for the
top ten restrictions (sample output shown in \tableref{Sample output from
SQL query showing percentages}):

\input{build/include-sample-sql-query}

\begin{table}[ht]
    \caption{Sample output from SQL query showing percentages}
    \empty{}\label{Sample output from SQL query showing
    percentages}
    \begin{tabular}[]{lrr}
        \tableline{}
        Restriction & Number of hits & Percentage of hits \\
        \tableline{}%
        \input{build/include-sample-sql-output}
        \tableline{}
    \end{tabular}
\end{table}
